---
title: "Munich Public Toilets"
format: 
  html:
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

# 

This project analyses the distribution of public toilets across Munich districts.

## Research Question

1.  How are public toilets distributed across Munich districts?

2.  Which districts have the highest and lowest number of public toilets?

3.  Is population density associated with public toilet availability?

## Data and licences

We use data on:

-   public toilets in Munich

-   population by district

-   area and population density by district



Our main data set:

  - "Bevölkerung in den Stadtbezirken" 
  (URL: https://opendata.muenchen.de/dataset/bevoelkerung-stadtbezirken) provided by the 
  statistical department of the regional capital Munich
  under the "Datenlizenz Deutschland – Namensnennung – Version 2.0" 
  as outlined in : www.govdata.de/dl-de/by-2-0 .
  It allows free universal use under the condition of properly naming the data set and its 
  creator.


Visualisation / map of Munich with subdivisions :
   
  - https://geoportal.muenchen.de/portal/opendata/ , also provided by the statistical department 
  of Munich under "Datenlizenz Deutschland – Namensnennung – Version 2.0" as stated above.
  
  The exact data we used can be downloaded here: 
  
  CVS data set with population:  (https://opendata.muenchen.de/dataset/e3f5dbd2-39cc-40cd-bc91-4bb49a0b1802/resource/a641ce6a-4e01-4f4b-9976-1ae6a47e3762/download/bevolkerung_bezirke_neu.csv).
  
  Map:
  (https://geoportal.muenchen.de/geoserver/gsm_wfs/ows?service=WFS&version=1.0.0&request=GetFeature&typeName=gsm_wfs:vablock_stadtbezirk&outputFormat=application/json).

  


## Number of Public Toilets

```{r}
library(tidyverse)
munich_data <- read.csv("data/stadtbezirke_final.csv")
```

```{r}
ggplot(munich_data, aes(x = reorder(sb_name, anzahl_wc), y = anzahl_wc)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Number of Public Toilets by District",
    x = "District",
    y = "Number of public toilets"
  )

```

## Public Toilets per 10,000 Residents

```{r}
ggplot(munich_data, aes(x = reorder(sb_name, wc_pro_10000), y = wc_pro_10000)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Public Toilets per 10,000 Residents",
    x = "District",
    y = "WC per 10,000 residents"
  )
```

## Population Density and Public Toilets

```{r}

ggplot(munich_data, aes(x = einwohnerdichte, y = anzahl_wc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Population Density and Number of Public Toilets",
    x = "Population density",
    y = "Number of public toilets"
  )
```

## Top 10 Districts by number of Public Toilets

```{r}
top10 <- munich_data |>
  arrange(desc(anzahl_wc)) |>
  slice_head(n = 10)

ggplot(
  top10,
  aes(
    x = reorder(sb_name, anzahl_wc),
    y = anzahl_wc
  )
) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Top 10 Districts by Number of Public Toilets",
    x = "District",
    y = "Number of Public Toilets"
  )

```

## Key Findings

## Conclusion

The results suggest that population density is not strongly associated with the number of public toilets. Some districts with high population density have relatively few public toilets, while others have many. This indicates that factors others than population density may influence the distribution of public toilets in Munich. Future analyses could include tourist numbers, public transport hubs, or district size.
